\documentclass[11pt,a4paper,twoside]{article}
\usepackage{package/lmuthesis}

\input{condition}
\ifthenelse{\boolean{release}}{
}{
    \usepackage{draftwatermark}
    \SetWatermarkText{DRAFT}
    \SetWatermarkScale{1}
}

\prof{Prof.\ Dr.\ Heinrich Hu{\ss}mann}
\title{Understanding and Predicting\\Web Browsing Behavior}
\author{Changkun Ou}
\email{hi@changkun.us}
\bearbeitungszeitraum{12.8.2018 bis 12.2.2019}
\betreuer{Malin Eiband and Dr. Daniel Buschek}
\aufgabenstellung{
    \begin{description}
        \item[Understanding and Predicting User Browsing Behavior]
 
        \item[Problem Statement]
        Understanding user behavior helps the designer optimize their product user experiences. Meanwhile, the user can benefit from a better product. Since user intents are elusive, changeable and sometimes even undetermined, 
        predict their behavior usually tricky and impossible. In most cases, a user may perform a series of wasted actions before reach an intended destination. 
        Nevertheless, user intents become clear step by step after performs a series of actions in a given context.

        \item[Scope of the Thesis] 
        Applying machine learning approaches in human-computer interaction gains its popularity. 
        The objective of this thesis is to use machine learning to develop techniques that 
        help a user better understand the user's behavior and benefits from it.
        As a first step, a literature review is needed for finding research questions in
        a specific research field.
        Based on the literature review, an interpretable machine learning model should be developed.
        Afterward, the thesis should design a reasonable experiment with 
        a suitable theoretical foundation for a user study of the developed model, 
        and give a comprehensive analysis of the developed model. 
        A demonstration software may be developed for explaining the model application.

        \item[Tasks] (1) Conduct a literature review to identify research questions 
        regarding a specific field of research that are of interest to researchers and practitioners.
        (2) Design a machine learning model and
        design an appropriate experiment with theoretical support to 
        justify model performance. A comprehensive analysis is needed for evaluating 
        its interpretability.
        (3) Develop an application as a demonstration of the model.
        \item[Requirements] Profound knowledge in human-computer interaction, 
        strong skills in mathematical modeling and machine learning approaches, 
        independent scientific work and creative problem solving,
        industrial experience in web development, and architecting.
        \item[Keywords] Clickstream, User Browsing Behavior, Machine Learning, Web
    \end{description}
}
\acknoledgement{
    I would like to appreciate Malin Eiband and Dr. Daniel Buschek for many of their great and 
    constructive discussions, suggestion around thesis topic selection, model statements,
    thesis structuring as well as their pacient of given supervision to the thesis. 
    The thesis would not be accomplished without them. Afterward, I am full of gratitude to 
    Prof. Hussmann and Prof. Butz for offering me an unexpected opportunity to study aboard in Germany 
    as well as their kindly helps regarding study and living in my academic period.
    Next, I wish to thank my best friend Yi Xia, schoolfellow Yifei Zhan and Xingying Chen, 
    former colleague Jin Luo, and prior supervisor Yingding Wang in a Master's course ``Human Computation''
    for their inspiring discussions, proofreading, and giving feedbacks surrounding the contents of my thesis.
    Finally, I will forever be beholden to my parents for their continuous supports 
    while my postgraduate study, since they dedicated their live to my better future.
}
\abstract{
Clickstream applications appeared at the end of last century and 
have proliferated the heart of our Internet world.
Trades, public opinions, and almost every web requests are precisely recorded 
on server-side log files.
The fundamental interaction between a web service client and server stands immutably, 
even though mobile devices have governed our daily life.
This thesis proposes a machine learning model that characterizes user browsing behavior 
while including multi-tab branching and backtrack actions in a browser instead of
web request-based clickstreams. The model is named the Action Path model (APM).
To justify the APM, a lab study is established and individuals' clickstream data is collected,
which consisted of chronologic URLs and corresponding stay durations for each URL.
The thesis designed nine different contexts given web browsing tasks for three mainstream websites 
based on the theory of information behavior.
Each website has three types of tasks: a goal-oriented task, fuzzy task and 
exploring browsing task. They characterize the corresponding three browsing 
behaviors.
The thesis seeks to achieve the following goals by analyzing the subject's trace from a lab study:
1) Understanding: identify if browsing behaviors are distinguishable and 
find common patterns that appear in an action path.
2) Classification: separate and report browsing behaviors on the web, which will help 
users to better understand their status.
3) Prediction: present the future click path in more than one step with the given context of
the browsing history in a session.
The quantitative analysis in this thesis indicates that goal-oriented, fuzzy, and exploring
browsing behaviors are classifiable with 100\% accuracy based on the combination of 
chronologic URLs and stay duration. 
The prediction performance of APM indicates higher than 60\% accuracy for 
three to five steps of future clickstream prediction.
The qualitative analysis of the APM indicates five observed patterns, 
including ``ring'',``star'', ``overlap'', ``hesitation'' and ``cluster'' patterns, which 
represent the patterns of an action path. 
To illustrate the application, a browser plugin is developed that proactively serves users,
and suggests predictions for the possible future user clicks.
Furthermore, the thesis discusses a generalized design of APM and plugin communication protocol. 
This discussion explores the possibility of formalizing the model and protocol as standard 
Web APIs to help designers and developers to improve and monitor the user experience of their products.
To the best knowledge of the author of the thesis, the proposed APM is the first model 
with a detailed study regarding web browsing behavior modeling 
based on clickstreams collected from the client side.
}

\begin{document}

\makecover
\makeaufgabenstellung
\makededication
\makeabstract
\maketoc
% \listoffigures
% \listoftables
\cleardoublepage

\input{contents/ch01-intro}
\input{contents/ch02-related}
\input{contents/ch03-model}
\input{contents/ch04-experiment}
\input{contents/ch05-analysis}
\input{contents/ch06-applications}
\input{contents/ch07-discussion}
\input{contents/ch08-conclusion}
\input{contents/ch09-appendix}

\input{literature/bib.tex}
\end{document}